Sequoidal Categories and Transfinite Games: A Coalgebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1. Full version with appendix available at \cite{RoundCorner}.}

### 2018-01-21 round-corner/paper/lipics-v2016-authors/without_appendix/sequoidal.tex
Started some new projects.

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Sequoidal Categories and Transfinite Games: A Coalgebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
\titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column

@@

\begin{proposition}\label{StrongMonoidalFunctorActual}
  $f\mapsto\oc f$ respects composition, so $\oc$ is a functor.  Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$ (this composite is an isomorphism, so $\epsilon$ is as well).
\end{proposition}
\begin{proof}
  See Appendix.
\end{proof}

@@

\appendix

\section{Proofs}

\subsection{Proof of Proposition \ref{StrongMonoidalFunctorActual}}

\begingroup
\def\thetheorem{\ref{StrongMonoidalFunctorActual}}
\begin{proposition}
  $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.  Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$.
\end{proposition}
\addtocounter{theorem}{-1}
\endgroup

In order to show that $\sigma\mapsto\oc\sigma$ respects composition, we need the following lemma:

\begin{lemma}\label{aFormulaForAlpha}
  Let $A$ be an object of $\C$.  Then $\alpha_A\from\oc A\to A\sequoid\oc A$ is equal to the following composite:
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\mu_A"]
        & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id_{\oc A}"]
          & A \tensor \oc A \arrow[r, "\wk_{A,\oc A}"]
            & A \sequoid \oc A
    \end{tikzcd}
    \]
\end{lemma}

\begin{proof}
  We may paste together the anamorphism diagrams for $\int_A$ and $\sigma_A$ to form the following diagram (where we shall omit subscripts where there is no ambiguity):
  \begin{equation*}
    \begin{tikzcd}[cramped]
      \oc A \arrow[r, "\alpha"] \arrow[d, "\sigma_A"']
        & A \sequoid \oc A \arrow[r, "\Delta"]
          &[-24pt] (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[r, "\dist\inv"]
            & (A \times A) \sequoid \oc A \arrow[d, "\id_{A\times A}\sequoid\sigma_A"] \\
      \oc(A\times A) \arrow[rrr, "\alpha"]
        &
          &
            & (A \times A) \sequoid \oc(A\times A) \\
      \oc A \tensor \oc A \arrow[rr, "\kappa_{A,A}"] \arrow[u, "\int_A"]
        &
          & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)) \arrow[r, "\dist\inv"]
            & (A\times A)\sequoid(\oc A \tensor \oc A) \arrow[u, "\id_{A\times A}\sequoid\int_A"']
    \end{tikzcd}
  \end{equation*}
  where we observe that the composites down the left and right hand sides (after inverting the lower arrows) are $\mu_A$ and $\id_{A\times A}\sequoid\mu_A$.

  Now note that we have the following commutative square:
  \[
    \begin{tikzcd}
      (A \times A) \sequoid \oc A \arrow[r, "\dist"] \arrow[d, "\id_{A\times A}\sequoid\mu_A"']
        & (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[d, "(\id\sequoid\mu)\times(\id\sequoid\mu)"] \\
      (A \times A) \sequoid (\oc A \tensor \oc A) \arrow[r, "\dist"']
        & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A))
    \end{tikzcd}
    \]

  (using the definition of $\dist$).  Putting this together with the diagram above, we get the following commutative diagram:
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\alpha"] \arrow[d, "\mu_A"']
        & A \sequoid \oc A \arrow[r, "\Delta"]
          & (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[d, "\id\sequoid\mu_A\times\id\sequoid\mu_A"] \\
      \oc A \tensor \oc A \arrow[rr, "\kappa_{A,A}"]
        & \cdots \arrow[r]
          & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A))
    \end{tikzcd}
    \]
  We now expand the definition of $\kappa_{A,A}$  and take the projections on to the first and second components, yielding the following two commutative diagrams:
  \[
    \begin{tikzcd}\label{firstProjectionDiagram}
      \oc A \arrow[rrr, "\alpha"] \arrow[d, "\mu_A"']
        &
          &
            & A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
      \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"]
        & (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"]
          & (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
            & A \sequoid (\oc A \tensor \oc A)
    \end{tikzcd}\tag{\textbf{1}}
    \]

  \begin{equation*}\label{secondProjectionDiagram}
    \begin{tikzcd}[cramped]
     \oc A \arrow[rrrr, "\alpha"] \arrow[d, "\mu_A"']
        &
          &
            &
              & A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
      \oc A \tensor \oc A \arrow[r, "\sym"']
        & \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id" yshift=0.4em]
          & (A \sequoid \oc A) \tensor \oc A \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
            & A \sequoid (\oc A \tensor \oc A) \arrow[r, "\id\sequoid\sym"']
              & A \sequoid (\oc A \tensor \oc A)
    \end{tikzcd}\tag{\textbf{2}}
  \end{equation*}

  From diagram \eqref{firstProjectionDiagram}, we construct the following commutative diagram:
  \[
    \begin{tikzcd}
      \oc A \arrow[rrr, "\alpha"] \arrow[d, rightsquigarrow, "\mu_A"'] \arrow[phantom, drrr, "\textbf{a}" xshift=0.9em]
        &
          &
            & A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
      \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"] \arrow[ddr, rightsquigarrow, "\der_A\tensor\id"'] \arrow[phantom, dr, "\textbf{b}" xshift=0.6em]
        & (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"] \arrow[d, "(\id\sequoid*)\tensor\id"] \arrow[phantom, dr, "\textbf{c}" xshift=0.3em]
          & (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"] \arrow[d, "(\id\sequoid*)\sequoid\id"] \arrow[phantom, dr, "\textbf{e}" xshift=0.3em]
            & A \sequoid (\oc A \sequoid \oc A) \arrow[d, "\id\sequoid(*\tensor\id)"] \\
      %
        & (A \sequoid I) \tensor \oc A \arrow[r, "\wk"] \arrow[d, "\run\tensor\id"] \arrow[phantom, dr, "\textbf{d}" xshift=0.3em]
          & (A \sequoid I) \sequoid \oc A \arrow[r, "\passoc\inv"], \arrow[d, "\run\tensor\id"] \arrow[phantom, r, "\textbf{f}" xshift=-0.6em, yshift=-1.0em]
            & A \sequoid (I \tensor \oc A) \arrow[dl, "\id\sequoid\lunit"] \\
      %
        & A \tensor \oc A \arrow[r, rightsquigarrow, "\wk"]
          & A \sequoid \oc A
            &
    \end{tikzcd}
    \]

  \textbf{a} is diagram \eqref{firstProjectionDiagram}.

  \textbf{b} commutes by the definition of $\der_A$.

  \textbf{c} and \textbf{d} commute because $\wk$ is a natural transformation.

  \textbf{e} commutes because $\passoc$ is a natural transformation.

  \textbf{f} commutes by one of the coherence conditions in the definition of a sequoidal category.

  We now observe that the composite of the three squiggly arrows is the composite we are trying to show is equal to $\alpha$; we have $\alpha$ along the top, so it will suffice to show that the composite
  \[
    \begin{tikzcd}
      \xi_A\;=\;\oc A \arrow[r, "\mu_A"]
        & \oc A \tensor \oc A \arrow[r, "*\tensor\id"]
          & I \tensor \oc A \arrow[r, "\lunit"]
            & \oc A
    \end{tikzcd}
    \]
  is equal to the identity.  We do this using diagram \eqref{secondProjectionDiagram}.  First we construct the diagram shown in Figure \ref{hugeDiagram1}.

  \begin{SidewaysFigure}
    \[
      \begin{tikzcd}[ampersand replacement=\&]
        \oc A \arrow[rrrrr, "\alpha"] \arrow[d, "\mu_A"'] \arrow[phantom, drrrrr, "\textbf{a}"]
          \&
            \&
              \&
                \& 
                  \& A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
        \oc A \tensor \oc A  \arrow[r, "\sym"] \arrow[d, "*\tensor\id"'] \arrow[phantom, dr, "\textbf{b}"]
          \& \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"] \arrow[d, "\id\tensor*"]
            \& (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"] \arrow[d, "\id\sequoid*"] \arrow[phantom, dr, "\textbf{d}"]
              \& (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"] \arrow[d, "\id\sequoid*"] \arrow[phantom, dr, "\textbf{e}"]
                \& A \sequoid (\oc A \tensor \oc A) \arrow[r, "\id\sequoid\sym"] \arrow[d, "\id\sequoid(\id\sequoid*)"] \arrow[phantom, dr, "\textbf{c}"]
                  \& A \sequoid (\oc A \tensor \oc A) \arrow[d, "\id\sequoid (*\sequoid\id)"] \\
        I \tensor \oc A \arrow[r, "\sym"] \arrow[d, "\lunit"'] \arrow[phantom, dr, "\textbf{g}"]
          \& \oc A \tensor I \arrow[r, "\alpha\tensor\id"] \arrow[d, "\runit"] \arrow[phantom, dr, "\textbf{f}"]
            \& (A \sequoid \oc A) \tensor I \arrow[r, "\wk"] \arrow[d, "\runit"] \arrow[phantom, dr, "\textbf{i}"]
              \& (A \sequoid \oc A) \sequoid I \arrow[r, "\passoc\inv"] \arrow[d, "\run"] \arrow[phantom, dr, "\textbf{j}"]
                \& A \sequoid (\oc A \tensor I) \arrow[r, "\id\sequoid\sym"] \arrow[d, "\id\sequoid\runit"] \arrow[phantom, dr, "\textbf{h}"]
                  \& A \sequoid (I \tensor \oc A) \arrow[d, "\id\sequoid\lunit"] \\
        \oc A \arrow[r, "\id"']
          \& \oc A \arrow[r, "\alpha"]
            \& A \sequoid \oc A \arrow[r, "\id"']
              \& A \sequoid \oc A \arrow[r, "\id"']
                \& A \sequoid \oc A \arrow[r, "\id"']
                  \& A \sequoid \oc A
      \end{tikzcd}
      \]
    \caption{
      \textbf{a} is diagram \eqref{secondProjectionDiagram}. \\[\baselineskip]
      \textbf{b} and \textbf{c} commute because $\sym$ is a natural transformation, \textbf{d} commutes because $\wk$ is a natural transformation and \textbf{e} commutes because $\passoc$ is a natural transformation.  \textbf{f} commutes because $\runit$ is a natural transformation. \\[\baselineskip]
      \textbf{g} and \textbf{h} commute by one of the coherence conditions for a symmetric monoidal category.  \textbf{i} commutes by one of the coherence conditions for $\wk$ in the definition of a sequoidal category and \textbf{j} commutes by one of the coherence conditions for $\passoc$ in the definition of a sequoidal category.
    }\label{hugeDiagram1}
  \end{SidewaysFigure}

  Now observe that the composite $\xi_A$ is running along the left hand side of Figure \ref{hugeDiagram1}, while $\id\sequoid\xi$ is running along the right.  Since we have $\alpha$ along the bottom, it follows by the uniqueness of $\fcoal{\cdot}$ that $\xi=\fcoal{\alpha}=\id_{\oc A}$.  
\end{proof}

Now we are ready to show that $f\mapsto\oc f$ respects composition.  Let $A,B,C$ be objects, let $f$ be a morphism from $A$ to $B$ and let $g$ be a morphism from $B$ to $C$.   Using Lemma \ref{aFormulaForAlpha} and the definition of $\oc f$, $\oc g$, we may construct a commutative diagram:
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\mu"] \arrow[d, "\oc f"']
      & \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
        & A \tensor \oc A \arrow[r, "f\tensor\id"]
          & B \tensor \oc A \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc\sigma"]
            & B \sequoid \oc A \;\times\; \oc A \sequoid B \arrow[d, "\id\sequoid\oc f\;\times\;\oc f\sequoid\id"] \\
    \oc B \arrow[r, "\mu"] \arrow[dd, "\oc g"']
      & \oc B \tensor \oc B \arrow[rr, "\der\tensor\id"]
        &
          & B \tensor \oc B \arrow[r, "\dec"] \arrow[d, "g\tensor\id"]
            & B \sequoid \oc B \;\times\; \oc B \sequoid B \\
    %
      &
        &
          & C \tensor \oc B \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc g"']
            & C \sequoid \oc B \;\times\; \oc B \sequoid C \arrow[d, "\id\sequoid\oc g\;\times\oc g\sequoid\id"] \\
    \oc C \arrow[r, "\mu"]
      & \oc C \tensor \oc C \arrow[rr, "\der\tensor\id"]
        &
          & C \tensor \oc C \arrow[r, "\dec"]
            & C \sequoid \oc C \;\times \oc C \sequoid C
  \end{tikzcd}
  \]
Here, the outermost (solid) shapes are the product of shapes that commute by the definition of $\oc f$, $\oc g$ (after we have replaced $\alpha_B$, $\alpha_C$ with the composite from Lemma \ref{aFormulaForAlpha}).  The smaller squares on the right hand side commute because $\dec$ is a natural transformation.  Since $\dec$ is an isomorphism, the two rectangles on the left commute as well.

Throwing away the right hand squares and adding some new arrows at the right, we arrive at the following commutative diagram:
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\comp{(f \tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc f"']
      &[72pt] B \tensor \oc A \arrow[r, "g \tensor\id"] \arrow[d, "\id\tensor\oc f"']
        & C \tensor \oc A \arrow[d, "\id\tensor\oc f"] \\
    \oc B \arrow[d, "\oc g"']
      & B \tensor\oc B \arrow[r, "g\tensor\id"] \arrow[d, "g\tensor\oc\tau"']
        & C \tensor \oc B \arrow[dl, "\id\tensor\oc g"] \\
    \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
      & C \tensor \oc C
        &
  \end{tikzcd}
  \]
We have just shown that the square on the left commutes.  The shapes on the right commute by inspection.  We now throw away the internal arrows and apply $\wk$ on the right hand side:
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\comp{((\comp g f)\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc f"']
      &[72pt] C \tensor \oc A \arrow[d, "\id\tensor\oc f"'] \arrow[r, "\wk"]
        & C \sequoid \oc A \arrow[d, "\id\sequoid\oc f"] \\
    \oc B \arrow[d, "\oc g"']
      & C \tensor \oc B \arrow[d, "\id\tensor\oc g"'] \arrow[r, "\wk"]
        & \oc C \sequoid \oc B \arrow[d, "\id\sequoid\oc g"] \\
    \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
      & C \tensor \oc C \arrow[r, "\wk"]
        & C \sequoid\oc C
  \end{tikzcd}
  \]
By Lemma \ref{aFormulaForAlpha}, the composite along the bottom is equal to $\alpha_C$.  Therefore, by uniqueness of $\fcoal{\cdot}$, we have
\[
  \comp{\oc g}{\oc f} = \fcoal{\comp{\wk}{\comp{((\comp g f)\tensor\id)}{\comp{(\der\tensor\id)}\mu}}} = \oc(\comp g f)
  \]
Therefore, $\oc$ is indeed a functor.

We now want to show that $\oc$ has the structure of a strong symmetric monoidal functor from $(\C,\times,1)$ to $(\C,\tensor,I)$.  The relevant morphisms are:
\[
  \int_{A,B}\from \oc A \tensor \oc B \to \oc (A \times B)
  \quad
  \epsilon\from I \to \oc 1
  \]
By hypothesis, these are both isomorphisms.  We just need to show that the appropriate coherence diagrams commute.  That is, for any games $A,B,C$, we need to show that the following diagrams commute:
\[
  \begin{tikzcd}
    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\assoc_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id_{\oc C}"']
      &[24pt] \oc A \tensor (\oc B \tensor \oc C) \arrow[d, "\id_{\oc A}\tensor\int_{B,C}"] \\
    \oc (A \times B) \tensor \oc C \arrow[d, "\int_{A\times B,C}"']
      & \oc A \tensor \oc(B \times C) \arrow[d, "\int_{A,B\times C}"] \\
    \oc ((A \times B) \times C) \arrow[r, "\oc\assoc_{\times,A,B,C}"']
      & \oc (A \times (B \times C))
  \end{tikzcd}
\]
\[
  \begin{tikzcd}
    I \tensor \oc A \arrow[r, "\varepsilon\tensor\id"]
      & \oc 1 \tensor \oc A \arrow[d, "\int_{1,A}"] \\
    \oc A \arrow[u, "\lunit_{\oc A}"] \arrow[r, "\oc\lunit_A"]
      & \oc (1 \times A)
  \end{tikzcd}\quad
  \begin{tikzcd}
    \oc A \tensor I \arrow[r, "\id\tensor\varepsilon"]
      & \oc A \tensor \oc 1 \arrow[d, "\int_{A,1}"] \\
    \oc A \arrow[r, "\oc\runit_A"] \arrow[u, "\runit_{\oc A}"]
      & \oc (A \times 1)
  \end{tikzcd}\quad
  \begin{tikzcd}
    \oc A \tensor \oc B \arrow[r, "\sym_{A,B}"] \arrow[d, "\int_{A,B}"']
      & \oc B \tensor \oc A \arrow[d, "\int_{B,A}"] \\
    \oc(A\times B) \arrow[r, "\oc\sym_{A,B}"]
      & \oc(B\times A)
  \end{tikzcd}
  \]

We first prove a small lemma, which gives us a simpler way to compute $\oc \sigma$ in the case that $\sigma$ is a morphism in $\C_s$.

\begin{lemma}\label{ocStrict}
  Let $A,B$ be objects of $\C_s$ and let $\sigma$ be a morphism from $A$ to $B$ in $\C_s$.  Then the following diagram commutes:
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\alpha_A"] \arrow[d, "\oc \sigma"']
        & A \sequoid \oc A \arrow[r, "\sigma\sequoid\id"]
          & B \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
      \oc B \arrow[rr, "\alpha_B"]
        &
          & B \sequoid \oc B
    \end{tikzcd}
    \]
\end{lemma}

\begin{proof}
  By the definition of $\oc \sigma$, we have the following commutative diagram:
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\mu_A"] \arrow[d, "\oc \sigma"']
        & \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
          & A \tensor \oc A \arrow[r, "\sigma\tensor\id"]
            & B \tensor \oc A \arrow[r, "\wk"]
              & B \sequoid \oc A \arrow[d, "\id_B\sequoid\oc\sigma"] \\
      \oc B \arrow[rrrr, "\alpha_B"]
        &
          &
            &
              & B \sequoid \oc B
    \end{tikzcd}
    \]
  Therefore, it will suffice to show that the following diagram (solid lines) commutes:
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\alpha_A"] \arrow[d, "\mu_A"']
        & A \sequoid \oc A \arrow[r, "\sigma\sequoid\id"]
          & B \sequoid \oc A \\
      \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
        & A \tensor \oc A \arrow[u, dotted, "\wk"] \arrow[r, "\sigma\tensor\id"]
          & B \tensor \oc A \arrow[u, "\wk"]
    \end{tikzcd}
    \]
  The left hand square commutes by Lemma \ref{aFormulaForAlpha}.  The right hand square commutes because $\wk$ is a natural transformation.
\end{proof}

To show that the first coherence diagram commutes, we define a composite $\eta_{A,B,C}$:
\settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
\begin{gather*}
  (\oc A \tensor \oc B) \tensor \oc C \constantwidthxrightarrow{\langle\id,\; \sym\rangle} ((\oc A \tensor \oc B) \tensor \oc C) \times (\oc C \tensor (\oc A \tensor \oc B)) \\
  \hspace{6pt}\cdots \constantwidthxrightarrow{((\comp{\dist\inv}{\kappa_{A,B}})\tensor\id)\times(\alpha_C\tensor\id)} (((A \times B) \sequoid (\oc A \tensor \oc B)) \tensor \oc C) \times ((C \sequoid \oc C) \tensor (\oc A \tensor \oc B)) \\
  \hspace{6pt}\cdots \constantwidthxrightarrow{\wk\times\wk} (((A \times B) \sequoid (\oc A \tensor \oc B)) \sequoid \oc C) \times ((C \sequoid \oc C) \sequoid (\oc A \tensor \oc B)) \\
  \hspace{6pt}\cdots \constantwidthxrightarrow{\passoc\inv\times\passoc\inv} ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid (\oc C \tensor (\oc A \tensor \oc B))) \\
  \hspace{6pt}\cdots \constantwidthxrightarrow{\id\times(\id\sequoid\sym)} ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid ((\oc A \tensor \oc B) \tensor \oc C))
\end{gather*}

Observe the similarity between the definition of $\eta_{A,B,C}$ and that of $\kappa_{A\times B,C}$.  Indeed, it may be easily verified that the following diagram commutes, using the definition of $\int_{A,B}$ as the anamorphism for $\comp{\dist\inv}{\kappa_{A,B}}$ and the fact that $\wk$, $\passoc$ and $\sym$ are natural transformations:
\begin{equation}\label{kreuz}
  \begin{tikzcd}
    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\eta_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id"']
      & ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \arrow[d, "(\id\sequoid(\int\tensor\id))\times (\id\sequoid(\int\tensor\id))"] \\
    \oc (A \times B) \tensor \oc C \arrow[r, "\kappa_{A\times B,C}"]
      & ((A \times B) \sequoid (\oc (A \times B) \tensor \oc C)) \times (C \sequoid (\oc (A \times B) \tensor \oc C))
  \end{tikzcd}\tag{\kreuz}
\end{equation}
Then we get the commutative diagram in Figure \ref{CoherenceOneWay}, which tells us that one of the two paths round the coherence diagram is the anamorphism of $\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\eta_{A,B,C}}}$.  We now show that the other path round the coherence diagram is the anamorphism of the same thing, which will prove that they are equal.

\begin{SidewaysFigure}
  \[
    \begin{tikzcd}[ampersand replacement=\&]
      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\comp{\dist\inv}{\eta_{A,B,C}}"] \arrow[d, "\int_{A,B}\tensor\id"'] \arrow[phantom, dr, "\textbf{a}"]
        \&[24pt] ((A \times B) \times C) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[r, "\assoc_\times\sequoid\id"] \arrow[d, "\id\sequoid(\int\tensor\id)"] \arrow[phantom, dr, "\textbf{b}"]
          \&[19pt] (A \times (B\times C)) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid(\int\tensor\id)"] \\
      \oc (A \times B) \tensor \oc C \arrow[r, "\comp{\dist\inv}{\kappa_{A\times B,C}}"] \arrow[d, "\int_{A\times B,C}"'] \arrow[phantom, dr, "\textbf{d}"]
        \& ((A \times B) \times C) \sequoid (\oc(A\times B)\tensor \oc C) \arrow[r, "\assoc_\times\sequoid\id"] \arrow[d, "\id\sequoid\int"] \arrow[phantom, dr, "\textbf{c}"]
          \& (A \times (B\times C)) \sequoid (\oc(A\times B)\tensor\oc C) \arrow[d, "\id\sequoid\int"] \\
      \oc((A\times B)\times C) \arrow[r, "\alpha_{(A\times B)\times C}"] \arrow[d, "\oc \assoc_\times"'] \arrow[phantom, drr, "\textbf{e}"]
        \& ((A\times B) \times C) \sequoid \oc ((A\times B)\times C) \arrow[r, "\assoc_\times\sequoid\id"]
          \& (A \times (B\times C)) \sequoid \oc (A \times(B \times C)) \arrow[d, "\id\sequoid\oc \assoc_\times"] \\
      \oc(A \times (B\times C)) \arrow[rr, "\alpha_{A\times(B\times C)}"]
        \&
          \& (A \times (B \times C)) \sequoid \oc (A \times (B \times C))
    \end{tikzcd}
    \]
  \caption{\textbf{a} commutes by Diagram \eqref{kreuz}, plus the fact that $\dist$ is a natural transformation.  \\[\baselineskip]
  \textbf{b} and \textbf{c} commute because $\assoc_\times$ is a natural transformation.  \\[\baselineskip]
  \textbf{d} commutes by the definition of $\int_{A\times B,C}$.  \\[\baselineskip]
  \textbf{e} commutes by Lemma \ref{ocStrict}.}\label{CoherenceOneWay}
\end{SidewaysFigure}

For this, we define a composite $\tilde{\eta}_{A,B,C}$:
\settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
\begin{gather*}
  \oc A \tensor (\oc B \tensor \oc C) \constantwidthxrightarrow{\langle\sym,\id\rangle} (\oc A \tensor (\oc B \tensor \oc C)) \times ((\oc B \tensor \oc C) \tensor \oc A) \\
  \hspace{6pt}\cdots \constantwidthxrightarrow{(\alpha_A\tensor\id)\times((\comp{\dist\inv}{\kappa_{B,C}})\tensor\id)} ((A \sequoid \oc A) \tensor (\oc B \tensor \oc C)) \times (((B \times C) \sequoid (\oc B \tensor \oc C)) \tensor \oc A) \\
  \hspace{6pt}\cdots \constantwidthxrightarrow{\wk\times\wk} ((A \sequoid \oc A) \sequoid (\oc B \tensor \oc C)) \times (((B \times C) \sequoid (\oc B \tensor \oc C)) \sequoid \oc A) \\
  \hspace{6pt}\cdots \constantwidthxrightarrow{\passoc\inv\times\passoc\inv} (A \sequoid (\oc A \tensor (\oc B \tensor \oc C))) \times ((B \times C) \sequoid ((\oc B \tensor \oc C) \tensor \oc A)) \\
  \hspace{6pt}\cdots \constantwidthxrightarrow{\id\times(\id\sequoid\sym)} (A \sequoid (\oc A \tensor (\oc B \tensor \oc C))) \times ((B \times C) \sequoid (A \tensor (\oc B \tensor \oc C))) \\
\end{gather*}

We get a commutative diagram:
\[
  \begin{tikzcd}
    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\eta_{A,B,C}}}"] \arrow[d, "\assoc_{A,B,C}"']
      &[78pt] (A \times (B \times C)) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
    \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\tilde{\eta}_{A,B,C}}}"] \arrow[d, "\id\tensor\int"']
      & (A \times (B \times C)) \sequoid (\oc A \tensor (\oc B \tensor \oc C)) \arrow[d, "\id\sequoid(\id\tensor\int)"] \\
    \oc A \tensor \oc(B \times C) \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\kappa_{A,B\times C}}}"] \arrow[d, "\int_{A,B\times C}"']
      & (A \times (B \times C)) \sequoid (\oc A \tensor \oc (B\times C)) \arrow[d, "\id\sequoid\int"] \\
    \oc (A \times (B \times C)) \arrow[r, "\alpha_{A\times(B\times C)}"]
      & (A \times (B \times C)) \sequoid \oc (A \times (B \times C))
  \end{tikzcd}
  \]

Commutativity of the top square is a long and fairly unenlightening exercise in the coherence conditions for symmetric monoidal categories and for sequoidal categories.  Commutativity of the middle and bottom squares are by similar arguments to the ones in Figure \ref{CoherenceOneWay}.  Therefore, the two branches of the coherence diagram are anamorphisms for the same thing, and so they are equal.

The proofs for the other three coherence diagrams are similar.

\subsection{Proof of Proposition \ref{itsMu}}

\begingroup
\def\thetheorem{\ref{itsMu}}
\begin{proposition}
  $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ has comultiplication given by $\mu_A\from\oc A \to \oc A\tensor\oc A$ and counit given by the unique morphism $\eta_A\from \oc A \to I$.
\end{proposition}
\addtocounter{theorem}{-1}
\endgroup

By the definition of $\CCom$, the comultiplication in $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ is given by the composite:
\[
  \oc A \xrightarrow{\oc\Delta} \oc (A \times A) \xrightarrow{\int_{A,A}\inv} \oc A \times \oc A
  \]
By Lemma \ref{ocStrict}, the morphism $\oc\Delta$ is equal to the morphism $\sigma_A$ defined above.  So this composite is equal to $\comp{\int_{A,A}}{\sigma_A}=\mu_A$.

The counit is a morphism $\oc A\to I$, so by uniqueness it must be equal to $\eta_A$.

\subsection{Proof of Theorem \ref{Coalgebra__CoCoCo}}

\begingroup
\def\thetheorem{\ref{Coalgebra__CoCoCo}}
\begin{theorem}
  Let $(\C,\C_s,J,\wk)$ be a sequoidal category satisfying all the conditions from Theorem \ref{StrongMonoidalFunctor}.  Let $A$ be an object of $\C$ (equivalently, of $\C_s$).  Then $\oc A$, together with the comultiplication $\mu_A$ and counit $\eta_A$, is the cofree commutative comonoid over $A$.
\end{theorem}
\addtocounter{theorem}{-1}
\endgroup

>>>>

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Sequoidal Categories and Transfinite Games: A Coalgebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1.  Full version with appendix available at \cite{RoundCorner}.}}
\titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column

@@

\begin{proposition}\label{StrongMonoidalFunctorActual}
  $f\mapsto\oc f$ respects composition, so $\oc$ is a functor.  Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$ (this composite is an isomorphism, so $\epsilon$ is as well).
\end{proposition}
\begin{proof}
    See Appendix to full version \cite{RoundCorner}
\end{proof}

@@
